---
title: "Simulation: Change in Mean"
author: "Kai Wenger"
date: "`r Sys.Date()`"
bibliography: paper.bib
biblio-style: "apalike"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The following simulations demonstrate that the implemented tests for a change in mean in a long-memory time series do what they are supposed. For this purpose, we replicate results of papers that published the implemented tests. We use $500$ Monte Carlo replications throuhout all simulations.

## Wilcoxon LM and self-normalized Wilcoxon test
First, we replicate a comparision of the Wilcoxon LM test by @dehling2013non and the self-normalized Wilcoxon test by @betken2016testing, which is published in Tables III to VI of @betken2016testing pp. 793-794. For the power simulations (Tables V and VI) we just consider the case that the break is in the middle of the sample ($\tau=0.5$ following their notation) and the break magnitude is $\Delta=2$. Note that $d=H-0.5$.

```{r, eval=FALSE,echo=TRUE}
set.seed(410)
# Parameter setting considered
T_grid              <- c(10,50,100,500)
d_grid              <- c(0.1,0.2,0.3,0.4)
N                   <- 500

# Generate array to save the results 
resultmat           <- array(NA, dim=c(length(T_grid),length(d_grid),4))
dimnames(resultmat) <- list(paste("T=",T_grid,sep=""),paste("d=",d_grid,sep=""),
                            paste(rep(c("WilcoxonLM","snWilcoxon"),2),c("size","size",
				"power, Delta=1, tau=0.5","power, Delta=1,tau=0.5"),sep=" "))

# Monte Carlo simulation
for(TTT in 1:length(T_grid))
{
  T <- T_grid[TTT]
  for(ddd in 1:length(d_grid))
  {
    d                 <- d_grid[ddd]
    result_vec        <- 0
    for(i in 1:N)
    {
    # Simulate a fractionally integrated (long-memory) time series of 
    # length T with memory d that is not subject to a shift.
    tseries     <- fracdiff::fracdiff.sim(n=T,d=d)$series
  
    # Simulate a fractionally integrated (long-memory) time series of 
    # length T with memory d that is subject to a shift in the middle of
    # the sample of magnitude 2.  
    changep     <- c(rep(0,T/2),rep(2,T/2))
    tseries2    <- tseries+changep
  
    # They suppose that d is known and not estimated.
    
    # Apply both functions on both time series.
    testIsize    <- wilcoxonLM(tseries,d=d)
    testIIsize   <- snwilcoxon(tseries,d=d)
    testIpower   <- wilcoxonLM(tseries2,d=d)
    testIIpower  <- snwilcoxon(tseries2,d=d)
    
    # Save if the tests reject at the 5% significance level.
    testIsize    <- testIsize["Teststatistic"]   > testIsize["95%"]
    testIIsize   <- testIIsize["Teststatistic"]  > testIIsize["95%"]
    testIpower   <- testIpower["Teststatistic"]  > testIpower["95%"]
    testIIpower  <- testIIpower["Teststatistic"] > testIIpower["95%"]
    
    result_vec   <- result_vec+c(testIsize,testIIsize,testIpower,testIIpower)
    }
  resultmat[TTT,ddd,] <- result_vec/N
  print(c(TTT,ddd))
  }
}
# Results
resultmat
```

This yields the following results

```{r, echo = TRUE, eval=FALSE}
> resultmat
, , WilcoxonLM size

      d=0.1 d=0.2 d=0.3 d=0.4
T=10  0.014 0.012 0.090 0.264
T=50  0.022 0.028 0.054 0.140
T=100 0.044 0.032 0.034 0.112
T=500 0.038 0.028 0.042 0.082

, , snWilcoxon size

      d=0.1 d=0.2 d=0.3 d=0.4
T=10  0.072 0.026 0.032 0.016
T=50  0.038 0.038 0.058 0.056
T=100 0.052 0.056 0.038 0.080
T=500 0.042 0.060 0.050 0.050

, , WilcoxonLM power, Delta=1, tau=0.5

      d=0.1 d=0.2 d=0.3 d=0.4
T=10  0.426 0.452 0.558 0.726
T=50  1.000 0.976 0.852 0.788
T=100 1.000 1.000 0.952 0.824
T=500 1.000 1.000 1.000 0.912

, , snWilcoxon power, Delta=1, tau=0.5

      d=0.1 d=0.2 d=0.3 d=0.4
T=10  0.522 0.426 0.214 0.130
T=50  0.980 0.908 0.648 0.464
T=100 0.994 0.948 0.792 0.508
T=500 1.000 1.000 0.944 0.628
```

Apart from some small Monte Carlo differences, our results are equivalent to those of @betken2016testing and show the same pattern. 

## Self-normalized sup-Wald test
Here, we replicate results for the self-normalized sup-Wald test proposed by @shao2011simple. More precisely, we replicate part of the results of Tables 2 and 3 from pp. 602-603 (Section 3) of @shao2011simple.
For the power simulations (Tables III) we just consider the case that the break is in the middle of the sample ($\tau=0.5$ following their notation) and the break magnitude is $\Delta=1$. The significance level is $\alpha\in[10\%,5\%]$.

```{r, eval=FALSE,echo=TRUE}
set.seed(410)
# Parameter setting considered
T_grid              <- c(100,400)
d_grid              <- c(0,0.2,0.4)
N                   <- 500

# Generate array to save the results 
resultmat           <- array(NA, dim=c(length(T_grid)*2,length(d_grid),2))
dimnames(resultmat) <- list(paste(rep(paste("T=",T_grid,sep=""),each=2),rep(c("10%","5%"),2)),
			    paste("d=",d_grid,sep=""),paste(rep(c("snsupwald"),2),
			    c("size","power, Delta=1, tau=0.5"),sep=" "))


# Monte Carlo simulation
for(TTT in 1:length(T_grid))
{
  T <- T_grid[TTT]
  for(ddd in 1:length(d_grid))
  {
    d                 <- d_grid[ddd]
    result_vec        <- 0
    for(i in 1:N)
    {
      # Simulate a fractionally integrated (long-memory) time series of 
      # length T with memory d that is not subject to a shift.
      tseries       <- fracdiff::fracdiff.sim(n=T,d=d)$series
      
      # Simulate a fractionally integrated (long-memory) time series of 
      # length T with memory d that is subject to a shift in the middle of
      # the sample of magnitude Delta=1.  
      changep       <- c(rep(0,T/2),rep(1,T/2))
      tseries2      <- tseries+changep
      
      # Estimate the long-memory parameter of both series with the local Whittle
      # estimator using the suggested bandwidth T^0.65. 
      d_est         <- LongMemoryTS::local.W(tseries, m=floor(1+T^0.65))$d
      d_est2        <- LongMemoryTS::local.W(tseries2, m=floor(1+T^0.65))$d
      
      # Apply the function on both time series.
      testIsize     <- snsupwald(tseries,d=d_est)
      testIpower    <- snsupwald(tseries2,d=d_est2)
      
      # Save if the tests reject at the 10% and 5% significance level.
      testIsize10   <- testIsize["Teststatistic"]  > testIsize["90%"]
      testIsize5    <- testIsize["Teststatistic"]  > testIsize["95%"]
      testIpower10  <- testIpower["Teststatistic"] > testIpower["90%"]
      testIpower5   <- testIpower["Teststatistic"] > testIpower["95%"]
      
      result_vec    <- result_vec+c(testIsize10,testIsize5,testIpower10,testIpower5)
    }
    resultmat[((2*TTT-1):2*TTT),ddd,] <- result_vec/N
    print(c(TTT,ddd))
  }
}
# Results
resultmat
```

This yields the following results

```{r, echo = TRUE, eval=FALSE}
> resultmat
, , snsupwald size

            d=0 d=0.2 d=0.4
T=100 10% 0.084 0.118 0.098
T=100 5%  0.050 0.056 0.048
T=400 10% 0.104 0.106 0.090
T=400 5%  0.056 0.048 0.046

, , snsupwald power, Delta=1, tau=0.5

            d=0 d=0.2 d=0.4
T=100 10% 0.712 0.382 0.208
T=100 5%  0.540 0.240 0.104
T=400 10% 0.996 0.702 0.234
T=400 5%  0.984 0.562 0.128
```

We observe that the results coincide with the results obtained in @shao2011simple.

## Sup-Wald fixed-b test
The first column of Table II (Section 5.1, p. 47) of @iacone2014fixed is replicated in the following.

```{r, eval=FALSE,echo=TRUE}
set.seed(410)
# Parameter setting considered
T_grid              <- c(128,256,512)
d_grid              <- c(0,-0.2,0.2,-0.4,0.4)
N                   <- 500

# Generate array to save the results 
resultmat           <- array(NA, dim=c(length(T_grid),length(d_grid),1))
dimnames(resultmat) <- list(paste("T=",T_grid,sep=""),paste("d=",d_grid,sep=""),
                            paste(rep(c("fixbsupw"),1),c("size"),sep=" "))

# Monte Carlo simulation
for(TTT in 1:length(T_grid))
{
  T <- T_grid[TTT]
  for(ddd in 1:length(d_grid))
  {
    d                 <- d_grid[ddd]
    result_vec        <- 0
    for(i in 1:N)
    {
    # Simulate a fractionally integrated (long-memory) time series of 
    # length T with memory d that is not subject to a shift.
    tseries     <- fracdiff::fracdiff.sim(n=T,d=d)$series
  
    # Estimate the long-memory parameter of both series with the local Whittle
    # estimator using the suggested bandwidth T^0.65. 
    d_est       <- LongMemoryTS::local.W(tseries, m=floor(1+T^0.65))$d
    
    # Apply the function on the time series.
    testIsize    <- fixbsupw(tseries,d=d_est)
    
    # Save if the tests reject at the 5% significance level.
    testIsize    <- testIsize["Teststatistic"] > testIsize["95%"]
    
    result_vec   <- result_vec+c(testIsize)
    }
  resultmat[TTT,ddd,] <- result_vec/N
  print(c(TTT,ddd))
  }
}
# Results
resultmat
```

This yields the following results

```{r, echo = TRUE, eval=FALSE}
> resultmat
, , fixbsupw size

        d=0 d=-0.2 d=0.2 d=-0.4 d=0.4
T=128 0.064  0.034 0.054  0.044 0.076
T=256 0.076  0.050 0.056  0.038 0.076
T=512 0.064  0.068 0.046  0.030 0.050
```

We observe that the results obtained are slightly different to those of @iacone2014fixed. If we had chosen another seed, they would have been closer to the previously simulated values. However, also in our simulation the test shows the correct pattern.

## CUSUM LM and simple CUSUM test
Table I (Section 4, p. 93) of @wenger2018simple is replicated in the following.

```{r, eval=FALSE,echo=TRUE}
set.seed(410)
# Parameter setting considered
T_grid              <- c(250,500,1000)
d_grid              <- c(0,0.2,0.4)
m_grid              <- c(0.7,0.75,0.8)
N                   <- 500

# Generate array to save the results 
resultmat           <- array(NA, dim=c(length(T_grid),length(d_grid)*length(m_grid),4))
dimnames(resultmat) <- list(paste("T=",T_grid,sep=""),paste(rep(paste("d=",d_grid,sep=""),
			length(m_grid)),",m=",rep(m_grid,each=3),sep=""),
			paste(rep(c("CUSUM_simple","CUSUM-LM"),2),
			c("size","size","power","power"),sep=" "))


# Monte Carlo simulation
for(TTT in 1:length(T_grid))
{
  T <- T_grid[TTT]
  for(mmm in 1:length(m_grid))
  {
  m                 <- m_grid[mmm]
    for(ddd in 1:length(d_grid))
    {
    d                 <- d_grid[ddd]
    result_vec        <- 0
      for(i in 1:N)
      {
        # Simulate a fractionally integrated (long-memory) time series of 
        # length T with memory d that is not subject to a shift.
        tseries     <- fracdiff::fracdiff.sim(n=T,d=d)$series
      
        # Simulate a fractionally integrated (long-memory) time series of 
        # length T with memory d that is subject to a shift in the middle of
        # the sample of magnitude Delta=1.  
        changep     <- c(rep(0,T/2),rep(1,T/2))
        tseries2    <- tseries+changep
      
        # Estimate the long-memory parameter of both series with the local Whittle
        # estimator using the suggested bandwidth T^m. 
        d_est       <- LongMemoryTS::local.W(tseries, m=floor(1+T^m))$d
        d_est2      <- LongMemoryTS::local.W(tseries2, m=floor(1+T^m))$d
        
        # Apply both functions on both time series.
        testIsize    <- CUSUM_simple(tseries,d=d)
        testIIsize   <- CUSUMLM(tseries,d=d,delta=m)
        testIpower   <- CUSUM_simple(tseries2,d=d)
        testIIpower  <- CUSUMLM(tseries2,d=d,delta=m)
        
        # Save if the tests reject at the 5% significance level.
        testIsize    <- testIsize["p-value"]         < 0.05
        testIIsize   <- testIIsize["Teststatistic"]  > testIIsize["95%"]
        testIpower   <- testIpower["p-value"]        < 0.05
        testIIpower  <- testIIpower["Teststatistic"] > testIIpower["95%"]
        
        result_vec   <- result_vec+c(testIsize,testIIsize,testIpower,testIIpower)
        }
  resultmat[TTT,(ddd+(mmm-1)*3),] <- result_vec/N
  print(c(TTT,ddd))
  }
  }
}
# Results
resultmat
```

This yields the following results

```{r, echo = TRUE, eval=FALSE}
> resultmat
, , CUSUM_simple size

       d=0,m=0.7 d=0.2,m=0.7 d=0.4,m=0.7 d=0,m=0.75 d=0.2,m=0.75 d=0.4,m=0.75 d=0,m=0.8 
T=250      0.038       0.036       0.026      0.046        0.044        0.032     0.040       
T=500      0.062       0.048       0.038      0.054        0.042        0.056     0.048       
T=1000     0.042       0.038       0.050      0.042        0.054        0.048     0.054       

	d=0.2,m=0.8 d=0.4,m=0.8
T=250	0.044       0.044
T=500	0.068       0.054
T=1000	0.038       0.038

, , CUSUM-LM size

       d=0,m=0.7 d=0.2,m=0.7 d=0.4,m=0.7 d=0,m=0.75 d=0.2,m=0.75 d=0.4,m=0.75 d=0,m=0.8 
T=250      0.038       0.044       0.022      0.048        0.056        0.030     0.040       
T=500      0.062       0.050       0.036      0.062        0.032        0.064     0.058       
T=1000     0.046       0.040       0.058      0.052        0.050        0.040     0.052       

	d=0.2,m=0.8 d=0.4,m=0.8
T=250	0.052       0.044
T=500	0.064       0.042
T=1000	0.058       0.032

, , CUSUM_simple power

       d=0,m=0.7 d=0.2,m=0.7 d=0.4,m=0.7 d=0,m=0.75 d=0.2,m=0.75 d=0.4,m=0.75 d=0,m=0.8
T=250          1       0.890       0.216          1        0.866        0.196         1       
T=500          1       0.988       0.276          1        0.990        0.292         1       
T=1000         1       1.000       0.338          1        1.000        0.328         1       

	d=0.2,m=0.8 d=0.4,m=0.8
T=250	0.852       0.228
T=500	0.982       0.238
T=1000	0.998       0.308

, , CUSUM-LM power

       d=0,m=0.7 d=0.2,m=0.7 d=0.4,m=0.7 d=0,m=0.75 d=0.2,m=0.75 d=0.4,m=0.75 d=0,m=0.8
T=250          1       0.910       0.254          1        0.896         0.24         1       
T=500          1       0.984       0.328          1        0.994         0.32         1       
T=1000         1       1.000       0.390          1        1.000         0.35         1       

	d=0.2,m=0.8 d=0.4,m=0.8
T=250	0.886       0.282
T=500	0.984       0.278
T=1000	1.000       0.356
```

We observe that the results coincide with Table I of @wenger2018simple.

## Fixed bandwidth CUSUM tests
Parts of Tables I to IV (pp. 5-8) of @wenger2019fixed is replicated in the following. We just simulate the tests for the bandwidth that are recommended by @wenger2019fixed (i.e. $b=0.1$, $M=10$).

```{r, eval=FALSE,echo=TRUE}
set.seed(410)
# Parameter setting considered
T_grid              <- c(250,500)
d_grid              <- c(-0.2,0,0.2,0.4)
N                   <- 500

# Generate array to save the results 
resultmat           <- array(NA, dim=c(length(T_grid),length(d_grid),8))
dimnames(resultmat) <- list(paste("T=",T_grid,sep=""),paste("d=",d_grid,sep=""),
                            paste(rep(c("fixed-b type-A","fixed-b type-B","fixed-m type-A",
				"fixed-m type-B"),2),c(rep("size",4),rep("power",4)),sep=" "))

# Monte Carlo simulation
for(TTT in 1:length(T_grid))
{
  T <- T_grid[TTT]
  for(ddd in 1:length(d_grid))
  {
    d                 <- d_grid[ddd]
    result_vec        <- 0
    for(i in 1:N)
    {
      # Simulate a fractionally integrated (long-memory) time series of 
      # length T with memory d that is not subject to a shift.
      tseries     <- fracdiff::fracdiff.sim(n=T,d=d)$series
      
      # Simulate a fractionally integrated (long-memory) time series of 
      # length T with memory d that is subject to a shift in the middle of
      # the sample of magnitude 2.  
      changep     <- c(rep(0,T/2),rep(sd(tseries),T/2))
      tseries2    <- tseries+changep
      
      # Estimate the long-memory parameter of both series with the local Whittle
      # estimator using the suggested bandwidth T^0.8. 
      d_est       <- LongMemoryTS::local.W(tseries, m=floor(1+T^0.8))$d
      d_est2      <- LongMemoryTS::local.W(tseries2, m=floor(1+T^0.8))$d
      
      # Apply both functions on both time series.
      testIsize    <- CUSUMfixed(tseries, d=d_est, procedure="CUSUMfixedb_typeA", bandw=0.1)
      testIIsize   <- CUSUMfixed(tseries, d=d_est, procedure="CUSUMfixedb_typeB", bandw=0.1)
      testIIIsize  <- CUSUMfixed(tseries, d=d_est, procedure="CUSUMfixedm_typeA", bandw=10)
      testIVsize   <- CUSUMfixed(tseries, d=d_est, procedure="CUSUMfixedm_typeB", bandw=10)
      testIpower   <- CUSUMfixed(tseries2, d=d_est2, procedure="CUSUMfixedb_typeA", bandw=0.1)
      testIIpower  <- CUSUMfixed(tseries2, d=d_est2, procedure="CUSUMfixedb_typeB", bandw=0.1)
      testIIIpower <- CUSUMfixed(tseries2, d=d_est2, procedure="CUSUMfixedm_typeA", bandw=10)
      testIVpower  <- CUSUMfixed(tseries2, d=d_est2, procedure="CUSUMfixedm_typeB", bandw=10)
      
      # Save if the tests reject at the 5% significance level.
      testIsize    <- testIsize["Teststatistic"]   > testIsize["95%"]
      testIIsize   <- testIIsize["Teststatistic"]  > testIIsize["95%"]
      testIIIsize  <- testIIIsize["Teststatistic"] > testIIIsize["95%"]
      testIVsize   <- testIVsize["Teststatistic"]  > testIVsize["95%"]
      testIpower   <- testIpower["Teststatistic"]  > testIpower["95%"]
      testIIpower  <- testIIpower["Teststatistic"] > testIIpower["95%"]
      testIIIpower <- testIIIpower["Teststatistic"]> testIIIpower["95%"]
      testIVpower  <- testIVpower["Teststatistic"] > testIVpower["95%"]
      
      result_vec   <- result_vec+c(testIsize,testIIsize,testIIIsize,testIVsize,testIpower.
			testIIpower,testIIIpower,testIVpower)
    }
    resultmat[TTT,ddd,] <- result_vec/N
    print(c(TTT,ddd))
  }
}
# Results
resultmat
```

This yields the following results

```{r, echo = TRUE, eval=FALSE}
> resultmat
, , fixed-b type-A size

      d=-0.2   d=0 d=0.2 d=0.4
T=250  0.010 0.046 0.064 0.094
T=500  0.012 0.054 0.106 0.072

, , fixed-b type-B size

      d=-0.2   d=0 d=0.2 d=0.4
T=250  0.044 0.052 0.042 0.064
T=500  0.034 0.070 0.066 0.052

, , fixed-m type-A size

      d=-0.2   d=0 d=0.2 d=0.4
T=250  0.030 0.042 0.034 0.070
T=500  0.044 0.056 0.074 0.056

, , fixed-m type-B size

      d=-0.2   d=0 d=0.2 d=0.4
T=250  0.032 0.042 0.034 0.066
T=500  0.044 0.056 0.082 0.050

, , fixed-b type-A power

      d=-0.2 d=0 d=0.2 d=0.4
T=250      1   1 0.870 0.458
T=500      1   1 0.966 0.450

, , fixed-b type-B power

      d=-0.2 d=0 d=0.2 d=0.4
T=250      1   1 0.732 0.282
T=500      1   1 0.890 0.322

, , fixed-m type-A power

      d=-0.2 d=0 d=0.2 d=0.4
T=250      1   1 0.816 0.364
T=500      1   1 0.964 0.378

, , fixed-m type-B power

      d=-0.2 d=0 d=0.2 d=0.4
T=250      1   1 0.786 0.322
T=500      1   1 0.942 0.346
```

Again, we observe that the results coincide with Tables I to IV of @wenger2019fixed.

## References